---
title: "Operationalization "
author: "Tanya Bonilla"
date: "12/11/2019"
output:
  html_document: default
  pdf_document: default
---

# Loading in the Data

We begin with normal procedure; by loading in any data and files that are needed for analysis.

```{r message=FALSE, error=FALSE, warning=FALSE, results='hide'}
library(knitr)
library(tidyverse)
library(MASS)

purl("p02_airbnb.Rmd", output = "second_del.r")
source("first_del.r")
source("second_del.r")
```

As I feel like there is more to discover in the  ***Airbnb: Data Modeling***, we will further explore the *New York Fields* data set.

## Creating a New Model & Cross-Validation

Let's look at and define the new_york_fields tibble we created in ***Data Modeling***. Here, we will look at the price compared to the neighborhood the data was cleansed from, the type of bed provided by the host, and the availability of the listing throughout the year. From the graph we can see that there is a positive correlation between availability and price. 
```{r}
new_york_fields$bed_type <- as.factor(new_york_fields$bed_type)

model <- lm(price ~ neighbourhood_group_cleansed + bed_type + availability_365, data = new_york_fields)
model

ggplot(model, aes(x = availability_365, y =price))+ geom_jitter() + geom_smooth(method= lm)
```
Now we will cross-validate the model we created by splitting the data by reating a 70-30 partition and storing 70% of the data in **train** and the other bit in **test**.
```{r}
set.seed(385)
sample_selection <- createDataPartition(new_york_fields$price, p = 0.70, list = FALSE)
train <- new_york_fields[sample_selection,]
test <- new_york_fields[-sample_selection,]
train_model <- lm(price ~ neighbourhood_group_cleansed + bed_type + availability_365, data = train)
predictions <- train_model %>% predict(test)
```

## Explanation of Our Findings
```{r expl}
summary(train_model)
R2(predictions, test$price)
MAE(predictions, test$price)
```
As we can see, R^2^ is ~0.022 which is much smaller than we would want; much smaller than the last model in the second deliverable. Along with MAE, which is much larger than we would want too as it is ~80.8. The p-value in the results did change in this case either meaning there must be some relationship that should be further explored. 

## Operationalization

  We can use the data that we have collected and models we have created to inform consumers of what places in New York are cheaper to look at when considering staying in New York. This could cause potential consumers to be more economical in their trips and be willing to use Airbnb more.
  
## Social Impact & Consequences
  Some consequences that could come from informing consumers about such findings though are that some hosts on Airbnb could lose revenue due to the change in consumer wants. Say their place is nice menaing their price is higher, then there is a chance a potential client could look elsewhere. Another consequence would be that small-business motels/inns or B8B's lose clientele as well. 
  
## What next...
When I first began this project, I had a vision to coompare hotel listings with those of Airbnb's, but I could not find a suitable dataset that would allow me to conduct such an analysis. A future goal for this assignment would be to compile data of hotel prices in New York over a span of time and compare them to those of Airbnb's. 
